The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
reflow
include years

### Temporal scale
#### Time window length and position
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for winter (starting at 1
January) and summer (starting at 3 August). The position of the time window was
shifted by 1-48 days, using a fixed time window length of 48 days. These new
time windows were iteratively used to partition data into two discrete seasons
(winter, summer) and generate multilayer networks.

>>>>

### Temporal scale
#### Time window length and position
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for summer (starting at 3 August 2017) and winter (starting at 1
January 2018). The position of the time window was
shifted by 1-48 days, using a fixed time window length of 48 days. These new
time windows were iteratively used to partition data into two discrete seasons
(summer and winter) and generate multilayer networks.
